### 2021-08-20 documentos/notas/notas_carlos.tex

\section{Krauss}

In order to study the Krauss operators corresponding to PCE's, it is enough to study 
the ones corresponding to generators, that is, the ones that leave 
have of the components invariant.

As a historical fact, the Krauss operators corresponding to one single qubit PCEs
are 
\begin{equation}
\{\openone/\sqrt2, \sigma_i/\sqrt2\}
\label{eq:kraus:PCE}
\end{equation}
(corresponding to the operation that leaves the component $\sigma_i$ invariant), 
see Eq. 8.95 of Chuang's book.  Visual inspection of the Krauss operators 
of two qubit PCEG (PCE generators) lead to the ansatz that 
the appropriate Krauss operators are 
\begin{equation}
\left\{\openone/\sqrt2, \left(\bigotimes_k \sigma_{i_k}\right)/\sqrt2\right\}. 
\label{}
\end{equation}

We shall first show that the aforementioned Kraus operators indeed produce a PCE. 
Notice that 
\begin{equation}
\sigma_i \sigma_j \sigma_i =a^i_{j} \sigma_j,
\label{}
\end{equation}
with $a$ the matrix that appears in 
\eref{eq:eigvals-PCE}. Next, consider the action of a channel with Krauss representation 
\eref{eq:kraus:PCE} on an $n$ qubit system with Bloch sphere representation \eref{eq:nqubit:bloch},
\begin{align}
\mcM[\rho] &= 
\frac{\openone}{\sqrt{2}} \rho\frac{\openone}{\sqrt{2}} 
 + 
\frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \rho
\frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \\
&=\frac12 \left(\rho + \bigotimes_k \sigma_{i_k} \rho \bigotimes_k \sigma_{i_k} \right)\\
&=\frac12 \rho
+ \frac12\sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \bigotimes_k  \sigma_{i_k} \sigma_{j_k}  \sigma_{i_k} \\
&=
\sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \frac{1+\prod_k a^{i_k}_{j_k}}{2} \bigotimes_k  \sigma_{j_k} . 
\end{align}
However, $(1+\prod_k a^{i_k}_{j_k})/2$ is 0 or 1, proving the channel is a PCE.

>>>>

\section{Kraus}

In order to study the Kraus operators corresponding to PCE's, it is enough to study 
the ones corresponding to generators, that is, the ones that leave 
have of the components invariant.

As a historical fact, the Kraus operators corresponding to one single qubit PCEs
are 
\begin{equation}
\{\1/\sqrt2, \sigma_i/\sqrt2\}
\label{eq:kraus:PCE}
\end{equation}
(corresponding to the operation that leaves the component $\sigma_i$ invariant), 
see Eq. 8.95 of Chuang's book.  Visual inspection of the Kraus operators 
of two qubit PCEG (PCE generators) lead to the ansatz that 
the appropriate Kraus operators are 
\begin{equation}
\left\{\1/\sqrt2, \left(\bigotimes_k \sigma_{i_k}\right)/\sqrt2\right\}. 
\label{}
\end{equation}

We shall first show that the aforementioned Kraus operators indeed produce a PCE. 
Notice that 
\begin{equation}
\sigma_i \sigma_j \sigma_i =a^i_{j} \sigma_j,
\label{}
\end{equation}
with $a$ the matrix that appears in 
\eqref{eq:eigvals-PCE}. Next, consider the action of a channel with Kraus representation 
\eqref{eq:kraus:PCE} on an $n$ qubit system with Bloch sphere representation \eqref{eq:nqubit:bloch},
\begin{align}
M[\rho] &= 
\frac{\1}{\sqrt{2}} \rho\frac{\1}{\sqrt{2}} 
 + 
\frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \rho
\frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \\
&=\frac12 \left(\rho + \bigotimes_k \sigma_{i_k} \rho \bigotimes_k \sigma_{i_k} \right)\\
&=\frac12 \rho
+ \frac12\sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \bigotimes_k  \sigma_{i_k} \sigma_{j_k}  \sigma_{i_k} \\
&=
\sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \frac{1+\prod_k a^{i_k}_{j_k}}{2} \bigotimes_k  \sigma_{j_k} . 
\end{align}
However, $(1+\prod_k a^{i_k}_{j_k})/2$ is 0 or 1, proving the channel is a PCE.
